### 2020-06-17 report/sections/evalconcl/concl/contributions.tex
Report: address NY comments

% PLACES
Our work has received positive feedback from academia.
The project has been accepted and published as 
\emph{Generating Interactive WebSocket Applications in TypeScript}
in Volume 314 of the Electronic Proceedings in Theoretical
Computer Science (EPTCS) \cite{PLACES2020}.
We were also invited to present a part of this work
at the 12th International Workshop on
Programming Language Approaches to Concurrency- \& 
Communication-cEntric Software (PLACES 2020).

>>>>

% PLACES
Our work has received positive feedback from academia.
The intitial part of this project was published as 
\emph{Generating Interactive WebSocket 
Applications in TypeScript} in Volume 314 of the Electronic Proceedings
in Theoretical Computer Science (EPTCS) \cite{PLACES2020},
in which I am the first and lead author.
The materials in \cref{chap:codegen,chap:node,chap:react}
are expanded from \cite{PLACES2020}.
We were also invited to present a part of this work
at the 12th International Workshop on
Programming Language Approaches to Concurrency- \& 
Communication-cEntric Software (PLACES 2020).

### 2020-06-17 report/sections/introduction/contributions.tex
Report: address NY comments

\begin{remark}
This project was published as \emph{Generating Interactive WebSocket 
Applications in TypeScript} in Volume 314 of the Electronic Proceedings
in Theoretical Computer Science (EPTCS) \cite{PLACES2020},
in which I am the first and lead author.

The materials in \cref{chap:codegen,chap:node,chap:react}
are revised from \cite{PLACES2020}.
The materials in 
\cref{chap:ext,chap:p2p,chap:theory,chap:impl,chap:eval}
are developed exclusively in this project by myself.
\end{remark}

>>>>

\begin{remark}
A part of this project was published as 
\emph{Generating Interactive WebSocket 
Applications in TypeScript} in Volume 314 of the Electronic Proceedings
in Theoretical Computer Science (EPTCS) \cite{PLACES2020},
in which I am the first and lead author.

The materials in \cref{chap:codegen,chap:node,chap:react}
are expanded from \cite{PLACES2020}.
The materials in 
\cref{chap:ext,chap:p2p,chap:theory,chap:impl,chap:eval}
are developed exclusively in this project by myself.
\end{remark}
